---
title: "Statistical analyses for peer review uncertainty study: Appendices"
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
library(dplyr)
library(tidyr)
library(stringr)
library(visdat) # for missing data visualisation
library(flextable)
library(ggplot2)
library(gridExtra)
source('99_functions.R') # for make_missing_data

# from 2_read_journal_data.R (after journal stuff is added)
load('data/2_data.RData')

# numbers from 3_analyses.Rmd
load('data/3_for_appendices.Rdata')
```

## Missing data

Here we look at item-missing data in the responses. We split by journal because _Epidemiology_ has six possible decisions,  whereas _BMJ Open_ has four and _F1000_ has only three.

```{r, include=FALSE}
# breaks for x-axis so that questions appear in same order as online questions
miss.breaks = c('Uncertainty 1',
                'Uncertainty 2',
                'Uncertainty 3',
                'Uncertainty 4',
                'Uncertainty 5',
                'Uncertainty 6',
                'Recommendation',
                'Paper title',
                'Time spent on review',
                'Gender',
                'Years in research',
                'Country',
                'Time between submission and review', # data from journals
                'Paper type',
                'Version number',
                'Editorial decision')
```

### BMJ Open

```{r missing_bmj_open, fig.width=9, fig.height=5}
bmj_miss = make_missing_plot(indata = data, injournal = 'BMJ Open')
bmj_miss$plot
```

### Epidemiology

```{r missing, fig.width=9, fig.height=5}
epi_miss = make_missing_plot(indata = data, injournal = 'Epidemiology')
epi_miss$plot
```

### F1000

```{r missing_f1000, fig.width=9, fig.height=5}
f1000_miss = make_missing_plot(indata = data, injournal = 'F1000')
f1000_miss$plot
```

#### Overall table of missing

```{r}
overall = bind_rows(bmj_miss$table, epi_miss$table, f1000_miss$table)
ftab = flextable(overall) %>%
  theme_box() %>%
  merge_v(j=1) %>%
  autofit()
ftab
```

The table rows are ordered by the journal and the number missing.


## Optional comments

We removed short comments like "thanks" or "none". The comments are ordered by the longest to shortest. The journal name is included.

```{r comments, results='asis'}
comments = filter(data, 
                  !is.na(q1_5),
                  !str_detect(tolower(q1_5), pattern = '^thank'),
                  !str_detect(tolower(q1_5), pattern = '^na$'),
                  !str_detect(tolower(q1_5), pattern = 'good luck.'),
                  !str_detect(q1_5, pattern = '^None'),
                  !str_detect(tolower(q1_5), pattern = '^no comment'),
                  !str_detect(tolower(q1_5), pattern = '^\\.\\.\\.\\.\\.\\.'),
                  !str_detect(tolower(q1_5), pattern = '^no further comment'),
                  !str_detect(tolower(q1_5), pattern = '^none$'),
                  !str_detect(tolower(q1_5), pattern = '^no other comment')
                  ) %>%
  mutate(words = str_count(q1_5, '\\w+'), # word count
         nchar = nchar(q1_5))
# stats on word counts
stats = summarise(comments, 
                  median = round(median(words)), 
                  min = min(words),
                  max = max(words))
#
#comments = arrange(comments, -nchar) %>% # longest to shortest - use for final version
comments = arrange(comments, recorded_date) %>% # by date, easier for me to track new comments
  select(journal, q1_5)
for (k in 1:nrow(comments)){
  cat('* ', comments$q1_5[k], ' (', comments$journal[k], ')\n', sep='')
}
```

The median number of words per comment was `r stats$median` with a range from `r stats$min` to `r stats$max` words.


```{r, include=FALSE}
# big plot for paper
p1 = bmj_miss$plot + ggtitle('BMJ Open') + theme(legend.position = 'none')
p2 = epi_miss$plot + ggtitle('Epidemiology') + theme(legend.position = 'none')
p3 = f1000_miss$plot + ggtitle('F1000')
jpeg('figures/item_missing.jpg', width=7, height=9, units='in', res=500, quality = 100)
grid.arrange(p1, p2, p3, ncol = 1, heights=c(1,1,1.1))
invisible(dev.off())
```


