---
title: "Statistical analyses for peer review uncertainty study"
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
library(binom) # for confidence intervals
library(tidyr)
library(stringr)
library(dplyr)
options(dplyr.summarise.inform = FALSE)
library(janitor)
library(flextable)
library(ggplot2)
library(gridExtra)
g.theme = theme_bw() + theme(panel.grid.minor = element_blank())
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
source('99_functions.R')
source('3_labels.R') # labels for recommendations

# combine the data sets of results from 4_run_bayes_models.R
source('5_combine_results.R')

# labels
model_labels = c('Model 0: No predictor','Model 1: Predictor associated with mean', 'Model 2a: Predictor\nassociated with uncertainty', 'Model 2b: Predictor\nassociated with uncertainty (reverse)')
model_labels_breaks = c('Model 0: No predictor','Model 1: Predictor\nassociated with mean', 'Model 2a: Predictor\nassociated with uncertainty', 'Model 2b: Predictor\nassociated with uncertainty (reverse)')
```


Here we show the results of the regression models that examined if uncertainty was associated with reviewer characteristics.

## Model fit

The model fit was assessed using ten-fold cross validation and the mean square error with a 95% confidence interval for the mean. 
Separate results are shown for each predictor. 
Results are shown for the complete case and imputed data. 
The key comparison is whether the mean square errors are smaller than the baseline model with no predictors (model 0). 

### Protocol (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'protocol')
```

### Reviewer's gender male (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'gender')
```


### Reviewer's gender female (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'female')
```

### Reviewer's time spent (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'review_time')
```

### Reviewer's experience (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'experience')
```

### Version (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'version')
```

All the submissions at Epidemiology were the first version and so this journal was not included in this analysis.



### Time difference from submission to review (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'time_diff')
```

### Number of words (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'n_words')
```

### Flesch readability (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'flesch')
```

### Dale-Chall readability (model fit)

```{r, fig.width=7, fig.height=3}
plot_mse(indata = xval, inpredictor = 'dale_chall')
```


## Model fit summary

The figure below summarises the model fit results as shows for each journal and predictor whether the predictor was associated with changes in the mean and/or uncertainty. 

```{r, fig.width=7}
source('5_plot_tile_summary_model.R')
tplot
```

At Epidemiology there were no protocols and all papers were the first version.


## Plots of fitted values

### Model without predictors

This is the baseline model (Model 0) where the only predictor is the reviewers' recommendations.

#### F1000, No predictors

```{r}
## plot fitted, results exported to figure folder ##
plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'dummy', no_predictor=TRUE, this_imputed = FALSE)
```

#### BMJ Open, No predictors

```{r}
## plot fitted, results exported to figure folder ##
plot_fitted(indata = fitted, inxval = xval, this_journal = 'BMJ Open', this_predictor = 'dummy', no_predictor=TRUE, this_imputed = FALSE)
```

#### Epidemiology, No predictors

```{r, fig.width=7}
## plot fitted, results exported to figure folder ##
plot_fitted(indata = fitted, inxval = xval, this_journal = 'Epidemiology', this_predictor = 'dummy', no_predictor=TRUE, this_imputed = FALSE)
```


#### Summary statistics

Here we use summary statistics to verify the fitted values from the models above. We include the modal percentage in each recommendation.

```{r summary, fig.width=9, fig.height=6}
source('5_plot_summary.R')
pplot
```


### Time to peer review

#### F1000, Time to peer review

```{r, fig.width=7, fig.height=5}
## plot fitted, results exported to figure folder ##
plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'time_diff', predictor_label = c('Baseline', 'Double time'), this_imputed = FALSE)
```

#### BMJ Open, Time to peer review

```{r, fig.width=7, fig.height=5}
## plot fitted, results exported to figure folder ##
plot_fitted(indata = fitted, inxval = xval, this_journal = 'BMJ Open', this_predictor = 'time_diff', predictor_label = c('Baseline', 'Double time'), this_imputed = FALSE)
```

### Male gender

#### F1000, gender

```{r, fig.width=7, fig.height=5}
## plot fitted, results exported to figure folder ##
plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'gender', predictor_label = c('Male = No', 'Male = Yes'), this_imputed = FALSE)
```

#### BMJ Open, gender

```{r, fig.width=7, fig.height=5}
## plot fitted, results exported to figure folder ##
plot_fitted(indata = fitted, inxval = xval, this_journal = 'BMJ Open', this_predictor = 'gender', predictor_label = c('Male = No', 'Male = Yes'), this_imputed = FALSE)
```

#### Epidemiology, gender

```{r, fig.width=7, fig.height=5}
## plot fitted, results exported to figure folder ##
epi_gender = plot_fitted(indata = fitted, inxval = xval, this_journal = 'Epidemiology', this_predictor = 'gender', predictor_label = c('Male = No', 'Male = Yes'), this_imputed = FALSE)
```

### Female gender

#### F1000, female gender

```{r, fig.width=7, fig.height=5}
## plot fitted, results exported to figure folder ##
plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'female', predictor_label = c('Female = No', 'Female = Yes'), this_imputed = FALSE)
```

#### BMJ Open, female gender

```{r, fig.width=7, fig.height=5}
## plot fitted, results exported to figure folder ##
plot_fitted(indata = fitted, inxval = xval, this_journal = 'BMJ Open', this_predictor = 'female', predictor_label = c('Female = No', 'Female = Yes'), this_imputed = FALSE)
```

#### Epidemiology, female gender

```{r, fig.width=7, fig.height=5}
## plot fitted, results exported to figure folder ##
epi_female = plot_fitted(indata = fitted, inxval = xval, this_journal = 'Epidemiology', this_predictor = 'female', predictor_label = c('Female = No', 'Female = Yes'), this_imputed = FALSE)
```

### Version

#### F1000, version

```{r, fig.width=7, fig.height=5}
## plot fitted, results exported to figure folder ##
f1000_version = plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'version', predictor_label = c('Version = 1', 'Version = 2+'), this_imputed = FALSE)
```

#### BMJ Open, version

```{r, fig.width=7, fig.height=5}
bmjopen_version = plot_fitted(indata = fitted, inxval = xval, this_journal = 'BMJ Open', this_predictor = 'version', predictor_label = c('Version = 1', 'Version = 2+'), this_imputed = FALSE)
```

```{r include = FALSE}
# combine results across journals
file = 'figures/fitted_version.jpg'
jpeg(file, width = 9.5, height = 9, units = 'in', res = 600, quality = 100)
  grid.arrange(f1000_version,
               bmjopen_version, nrow=2)
invisible(dev.off())
```

### Protocol

#### F1000, protocol

```{r, fig.width=7, fig.height=5}
f1000_protocol = plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'protocol', predictor_label = c('Protocol = No', 'Protocol = Yes'), this_imputed = FALSE)
```

#### BMJ Open, protocol

```{r, fig.width=7, fig.height=5}
bmjopen_protocol = plot_fitted(indata = fitted, inxval = xval, this_journal = 'BMJ Open', this_predictor = 'protocol', predictor_label = c('Protocol = No', 'Protocol = Yes'), this_imputed = FALSE)
```

### Number of words

#### F1000, number of words

```{r, fig.width=7, fig.height=5}
f1000_protocol = plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'n_words', predictor_label = c('Baseline', '+2000 words'), this_imputed = FALSE)
```

### Flesch readability

#### F1000, Flesch readability

```{r, fig.width=7, fig.height=5}
f1000_protocol = plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'flesch', predictor_label = c('Baseline', '+10'), this_imputed = FALSE)
```

### Dale-Chall readability

#### F1000, Dale-Chall readability

```{r, fig.width=7, fig.height=5}
f1000_protocol = plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'dale_chall', predictor_label = c('Baseline', '+5'), this_imputed = FALSE)
```


### Reviewer's time spent

#### F1000, reviewer's time spent

```{r, fig.width=7, fig.height=5}
f1000_time_spent = plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'review_time', predictor_label = c('Reference', 'Double'), this_imputed = FALSE)
```

#### BMJ Open, reviewer's time spent

```{r, fig.width=7, fig.height=5}
bmjopen_time_spent = plot_fitted(indata = fitted, inxval = xval, this_journal = 'BMJ Open', this_predictor = 'review_time', predictor_label = c('Reference', 'Double'), this_imputed = FALSE)
```

#### Epidemiology, reviewer's time spent

```{r, fig.width=7, fig.height=5}
epidemiology_time_spent = plot_fitted(indata = fitted, inxval = xval, this_journal = 'Epidemiology', this_predictor = 'review_time', predictor_label = c('Reference', 'Double'), this_imputed = FALSE)
```

### Reviewer's experience

#### F1000, reviewer's experience

```{r, fig.width=7, fig.height=5}
f1000_experience = plot_fitted(indata = fitted, inxval = xval, this_journal = 'F1000', this_predictor = 'experience', predictor_label = c('Reference', '+5 years'), this_imputed = FALSE)
```

#### Epidemiology, reviewer's experience

```{r, fig.width=7, fig.height=5}
epidemiology_experience = plot_fitted(indata = fitted, inxval = xval, this_journal = 'Epidemiology', this_predictor = 'experience', predictor_label = c('Reference', '+5 years'), this_imputed = FALSE)
```


#### BMJ Open, reviewer's experience

```{r, fig.width=7, fig.height=5}
bmjopen_experience = plot_fitted(indata = fitted, inxval = xval, this_journal = 'BMJ Open', this_predictor = 'experience', predictor_label = c('Reference', '+5 years'), this_imputed = FALSE)
```

## Parameter estimates

The tables below show the parameter estimates with the 95% confidence intervals and Bayesian posterior probability.

Selected models only. Complete case estimates.

### F1000, version

```{r}
tab = make_table(indata = tables, this_journal = 'F1000', this_predictor = 'version', predictor_label = c('Version = 1', 'Version = 2+'), this_imputed = FALSE, model_labels = model_labels)
tab
```

### BMJ Open, reviewer's time spent

```{r}
tab = make_table(indata = tables, this_journal = 'BMJ Open', this_predictor = 'review_time', predictor_label = c('Baseline', 'Doubling'), this_imputed = FALSE, model_labels = model_labels)
tab
```

### Epidemiology, gender

```{r}
tab = make_table(indata = tables, this_journal = 'Epidemiology', this_predictor = 'gender', predictor_label = c('Male = No', 'Male = Yes'), this_imputed = FALSE, model_labels = model_labels)
tab
```

<!--- bespoke plots for paper --->

```{r bespoke}
## epidemiology female gender
epi_gender = epi_female +
  ggtitle('Epidemiology, gender')+
  theme(legend.position = 'right')
## bmj open protocol
bmjopen_protocol = bmjopen_protocol +
  ggtitle('BMJ Open, protocol')+
  theme(legend.position = 'right')
jpeg('figures/fitted_paper.jpg', width=10, height=6, units='in', quality=100, res=500)
grid.arrange(epi_gender, bmjopen_protocol, ncol=2, widths=c(1.2,1))
invisible(dev.off())
```
