---
title: "Compare the results from the complete case and imputed results"
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
# 
# Feb 2024
source('3_colours.R')
library(ggplot2)
g.theme = theme_bw() + theme(panel.grid.minor = element_blank())
library(dplyr)

# combine the data sets of results from 4_run_bayes_models.R
source('5_combine_results.R')
```

# Plots of parameter estimates and 95% credible intervals for complete case and imputed data

There's a separate panel for each model number.

```{r function, include=FALSE}
# plots of parameter estimates, separate facets for alpha, zeta, and beta
run_one_plot = function(this_journal, this_predictor, est_limits = NULL){
f = filter(tables, journal == this_journal, predictor == this_predictor) %>%
  filter(parameter != 'alpha[1]') %>%
  mutate(
  facet = case_when(
    model == 1 ~ '0',
    model == 2 ~ '1',
    model == 3 ~ '2a',
    model == 4 ~ '2b'
  ),  
    imputed = case_when(
    imputed == TRUE ~ "Imputed",
    imputed == FALSE ~ "Complete case"
  ))
plot = ggplot(data = f, aes(x=parameter, y=mean, ymin=lower, ymax=upper, col=imputed))+
  geom_point(position = position_dodge(width=0.4))+
  geom_errorbar(width=0, position = position_dodge(width=0.4))+
  ylab('Estimate')+
  scale_color_manual(NULL, values=c('darkseagreen3','darkorange2'))+
  xlab('')+
  facet_wrap(~facet, scales='free_y')+
  coord_flip()+
  g.theme+
  theme(legend.position = 'top')
#
if(!is.null(est_limits)){
  plot = plot + coord_flip(ylim = est_limits)
}
#
return(plot)
}
```

### BMJ Open, gender

```{r, fig.width=7, fig.height=7}
run_one_plot('BMJ Open', 'gender')
```

### BMJ Open, experience

```{r, fig.width=7, fig.height=7}
run_one_plot('BMJ Open', 'experience')
```

### BMJ Open, time taken on review

```{r, fig.width=7, fig.height=7}
run_one_plot('BMJ Open', 'review_time')
```


### BMJ Open, version

```{r, fig.width=7, fig.height=7}
run_one_plot('BMJ Open', 'version')
```

### BMJ Open, time to peer review

```{r, fig.width=7, fig.height=7}
run_one_plot('BMJ Open', 'time_diff')
```

### BMJ Open, protocol

```{r, fig.width=7, fig.height=7}
run_one_plot('BMJ Open', 'protocol')
```

### F1000, gender

```{r, fig.width=7, fig.height=7}
run_one_plot('F1000', 'gender')
```

### F1000, experience

```{r, fig.width=7, fig.height=7}
run_one_plot('F1000', 'experience')
```

### F1000, time taken on review

```{r, fig.width=7, fig.height=7}
run_one_plot('F1000', 'review_time')
```


### F1000, version

```{r, fig.width=7, fig.height=7}
run_one_plot('F1000', 'version')
```

### F1000, time to peer review

```{r, fig.width=7, fig.height=7}
run_one_plot('F1000', 'time_diff')
```

### F1000, protocol

```{r, fig.width=7, fig.height=7}
run_one_plot('F1000', 'protocol', est_limits=c(-1,6)) # had to limit
```

The estimates for zeta[1] in model 1 were very uncertain and so the plot has been truncates.


### Epidemiology, gender

```{r, fig.width=7, fig.height=7}
run_one_plot('Epidemiology', 'gender', est_limits=c(-1,10)) # had to limit
```

The estimates for zeta[1] in model 1 were very uncertain and so the plot has been truncates.

### Epidemiology, experience

```{r, fig.width=7, fig.height=7}
run_one_plot('Epidemiology', 'experience')
```

### Epidemiology, time taken on review

```{r, fig.width=7, fig.height=7}
run_one_plot('Epidemiology', 'review_time')
```

### Epidemiology, time to peer review

```{r, fig.width=7, fig.height=7}
run_one_plot('Epidemiology', 'time_diff')
```



# Compare fitted results for best model 

Comparing the probability estimates for the complete case and imputed data.

## BMJ and protocol ##


```{r, fig.width=7, fig.height=7}
ncat = 4
xlab = ''
alabels = breaks_bmj_return
colours = colours_bmj
legend_lab = 'Considered\nrecommendations'
margin = c(0,0,0,0)
predictor_label = c('Protocol = No', 'Protocol = Yes')
#
f = filter(fitted, journal=='BMJ Open', predictor == 'protocol', innum <=1, model == 3) %>%
  select(-predictor) %>%
  mutate(imputed = case_when(
    imputed == TRUE ~ "Imputed",
    imputed == FALSE ~ "Complete case"
  ),
  predictor = recommendation >= ncat + 1,
  recommendation = ifelse(predictor==TRUE, recommendation-ncat, recommendation), 
  facet = case_when(
    predictor == FALSE ~ 1, # reference category
    predictor == TRUE ~ 2
  ),
  facet = factor(facet, levels=1:2, labels = predictor_label)) # to give correct ordering)
#
fitted_plot = ggplot(data = f, aes(x=recommendation, y=median, fill=factor(uncertainty)))+
  geom_bar(stat='identity', position='stack', width = 0.99)+
  ylab('Probability')+
  xlab(xlab)+
  scale_x_continuous(breaks=1:ncat, labels=alabels, expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0))+
  coord_cartesian(ylim=c(0,1))+ # because numbers are sometimes fractionally short/over
  scale_fill_manual(legend_lab, labels=alabels, values=colours)+
  theme_bw()+
  facet_wrap(~facet+imputed)+
  theme(panel.grid.minor = element_blank(), 
        axis.text.x = element_text(angle=45, hjust=1),
        plot.margin = margin(t = margin[1], r = margin[2], b = margin[3], l = margin[4], unit = "pt"),
        legend.position = 'top')
fitted_plot

# export 
jpeg('figures/imputed_bmj_protocol.jpg', width = 7, height = 7, units= 'in', res=500, quality=100)
print(fitted_plot)
invisible(dev.off())

```

## Epidemiology and gender 

```{r, fig.width=7, fig.height=7}
ncat = 5
alabels = breaks_epi_no_none_return
colours = colours_epi_no_none
legend_lab = 'Considered\nrecommendations'
margin = c(0,0,0,0)
predictor_label = c('Male = No', 'Male = Yes')
predictor_label = rev(predictor_label) # as it's model 4
#
f = filter(fitted, journal=='Epidemiology', predictor == 'gender', innum <=1, model == 4) %>%
  select(-predictor) %>%
  mutate(imputed = case_when(
    imputed == TRUE ~ "Imputed",
    imputed == FALSE ~ "Complete case"
  ),
  predictor = recommendation >= ncat + 1,
  recommendation = ifelse(predictor==TRUE, recommendation-ncat, recommendation), 
  facet = case_when(
    predictor == FALSE ~ 1, # reference category
    predictor == TRUE ~ 2
  ),
  facet = factor(facet, levels=1:2, labels = predictor_label)) # to give correct ordering)
#
fitted_plot = ggplot(data = f, aes(x=recommendation, y=median, fill=factor(uncertainty)))+
  geom_bar(stat='identity', position='stack', width = 0.99)+
  ylab('Probability')+
  xlab(xlab)+
  scale_x_continuous(breaks=1:ncat, labels=alabels, expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0))+
  coord_cartesian(ylim=c(0,1))+ # because numbers are sometimes fractionally short/over
  scale_fill_manual(legend_lab, labels=alabels, values=colours)+
  theme_bw()+
  facet_wrap(~facet+imputed)+
  theme(panel.grid.minor = element_blank(), 
        axis.text.x = element_text(angle=45, hjust=1),
        plot.margin = margin(t = margin[1], r = margin[2], b = margin[3], l = margin[4], unit = "pt"),
        legend.position = 'top')
fitted_plot

# export 
jpeg('figures/imputed_epi_gender.jpg', width = 7, height = 7, units= 'in', res=500, quality=100)
print(fitted_plot)
invisible(dev.off())
```
